Title

### 2015-12-09 paper/paper.tex
lots of stuff on order learning

\subsection{Subgraph Ordering}
\subsection{Discrete Optimizations}

Subgraph ordering solves the problem of ordering a set of AMR sentences.

>>>>

\subsection{Subgraph Ordering}

Once we have split a merged graph into a partition of $p$ sentences, there are
$s!$ ways to order the sentences. Ideally, there exists some ordering of the
sentences that communicates the ideas of the merged graph in the best possible
way. Subgraph ordering is the problem of finding this optimal ordering.

Once again, we assumed that the ordering of sentences in the dataset was the
optimal ordering for that paragraph, so we needed to create non-optimal
examples to train on. This was done by randomly reordering the sentences for
$k=20$ reorderings for each paragraph.

We trained a Ridge regression model on the dataset. For the labels of the
training examples, we used the unnormalized Kendall's tau coefficient to
determine the distance between a given ordering and the optimal.

As noted in Related Work, our ordering model does not require the number of
sentences to be fixed to a particular value. If it were to impose such a
requirement, then the subgraph selection, which is further upstream in our
pipeline, may not be able to find its optimal partitioning simply because it
was a partitioning into a different number of sentences. As a result, our model
could not rely on any features that deal with particular sentences (e.g. the
similarity between the second and fifth sentences). So, we tried to use
features that would generalize to paragraphs of any length, but would still
vary with the ordering of those sentences within the paragraph, and all
features had to be summarized (mean, standard deviation, min, max) over the
paragraph. Features included the Jaccard similarity between adjancent
sentences, between sentences that are two sentences apart, and the Jaccard
similarity between the union of adjacent sentences and the overall paragraph.

\subsection{Discrete Optimizations}
